---
title: "Fit allometric growth models"
author: "Max Lindmark"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
  pdf_document: default
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---

```{r setup, include = FALSE, cache=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 12,
  fig.asp = 0.618,
  fig.align ='center'
)
```

# Allometric growth models
log(G) ~ log(L) * Area, with individual and year-varying intercepts, and use loo to compare them.

### Load libraries
```{r libraries and settings, message=FALSE}
# Load libraries (install first if needed)
library(tidyverse); theme_set(theme_classic(base_size = 12))
library(brms)
library(nlstools)
library(viridis)
library(bayesplot)
library(tidylog)
library(tidybayes)
library(RColorBrewer)
library(patchwork)
library(modelr)
library(janitor)

# Print package versions for versions
sessionInfo() 

# For parallel processing
options(mc.cores = parallel::detectCores()) 
```

### Read data
```{r}
d <- read.csv("data/for_fitting/growth_scaling_dat.csv")
```

### Fit models
I'm following the multilevel model vignette here: https://cran.r-project.org/web/packages/brms/index.html
And this one for specifying random structure: https://discourse.mc-stan.org/t/levels-within-levels/8814/3
https://stats.stackexchange.com/questions/400700/why-do-we-do-crossed-vs-nested-vs-other-random-effects
https://stackoverflow.com/questions/29717308/how-do-i-code-the-individual-in-to-an-lme4-nested-model

https://cran.r-project.org/web/packages/insight/vignettes/insight.html
See the insight package for verifying model structure

M0: Prior predictive check: Warm+Cold merged
```{r M0: Prior predictive check: Warm+Cold merged}
prior0 <-
  prior(normal(500, 100), nlpar = "alpha") +
  prior(normal(-1.2, 0.3), nlpar = "theta")
  
M0fmbt <- brm(
  bf(growth ~ alpha*length^theta, alpha ~ 1, theta ~ 1, nl = TRUE),
  data = d, family = student(),
  prior = prior0,
  sample_prior = "only", 
  iter = 4000, thin = 1, cores = 3, chains = 3, seed = 9)

# From add_fitted_draws {tidybayes}	which I use for the general predictions
# add_predicted_draws adds draws from posterior predictions to the data. It corresponds to ... or brms::predict.brmsfit() in brms.
pp <- conditional_effects(M0fmbt, method = "posterior_predict")

plot(pp, plot = FALSE)[[1]] +
  labs(y = expression(paste("Growth [%", yr^-1, "]")), x = "Length [cm]")

ggsave("figures/supp/growth_prior_pred_check.png", width = 6.5, height = 6.5, dpi = 600)
```

M1: All parameters area-specific
```{r M1: All parameters area-specific}
prior <-
  prior(normal(500, 100), nlpar = "alphaW") +
  prior(normal(500, 100), nlpar = "alphaC") +
  prior(normal(-1.2, 0.3), nlpar = "thetaW") +
  prior(normal(-1.2, 0.3), nlpar = "thetaC")

ptm <- proc.time()
m1 <- brm(bf(growth ~ areaW*alphaW*length^thetaW + areaC*alphaC*length^thetaC, 
             alphaW ~ 1 + (1|birth_year/ID), # parameter varying by ID within birth_year
             alphaC ~ 1 + (1|birth_year/ID), # parameter varying by ID within birth_year
             thetaW + thetaC ~ 1, nl = TRUE),
           family = student(),
           data = d, prior = prior, iter = 4000, cores = 3, chains = 3,
           seed = 9, save_pars = save_pars(all = TRUE),
           control = list(adapt_delta = 0.99))
proc.time() - ptm
# user   system  elapsed 
# 95.962   16.307 6181.922 

# summary(m1)
# plot(m1)
# prior_summary(m1)

# Save model object to not have to rerun it...
# saveRDS(m1, "output/growth_scaling/m1.rds")
# m1 <- readRDS("output/growth_scaling/m1.rds")

prior_summary(m1)
```

M2: Common theta parameter
```{r M2: Common theta parameter}
prior2 <-
  prior(normal(500, 100), nlpar = "alphaW") +
  prior(normal(500, 100), nlpar = "alphaC") +
  prior(normal(-1.2, 0.3), nlpar = "theta")
 
ptm <- proc.time()
m2 <- brm(bf(growth ~ areaW*alphaW*length^theta + areaC*alphaC*length^theta, 
             alphaW ~ 1 + (1|birth_year/ID), # parameter varying by ID within birth_year
             alphaC ~ 1 + (1|birth_year/ID), # parameter varying by ID within birth_year
             theta ~ 1, nl = TRUE),
           family = student(),
           data = d, prior = prior2, iter = 4000, cores = 3, chains = 3,
           seed = 9, save_pars = save_pars(all = TRUE),
           control = list(adapt_delta = 0.99))
proc.time() - ptm


# summary(m2)
# plot(m2)
# prior_summary(m2)

# Save model object to not have to rerun it...
# saveRDS(m2, "output/growth_scaling/m2.rds")
# m2 <- readRDS("output/growth_scaling/m2.rds")
```

### Compare models
```{r compare models}
# Compare models: https://mc-stan.org/loo/articles/loo2-example.html
# Expected log pointwise predictive density

# loo_m1 <- loo(m1, moment_match = TRUE)
# loo_m2 <- loo(m2, moment_match = TRUE)
loo_m1 <- loo(m1, moment_match = TRUE)
loo_m2 <- loo(m2, moment_match = TRUE)

plot(loo_m1)
abline(a = 0.7, b = 0)

plot(loo_m2)
abline(a = 0.7, b = 0)

loo_compare(loo_m1, loo_m2)
# elpd_diff se_diff
# m1  0.0       0.0   
# m2 -2.7       4.4
```

### Figures
#### Main fiures
```{r main fiures}
pal <- brewer.pal(n = 6, name = "Paired")[c(2, 6)]
# m1 <- readRDS("output/growth_scaling/m1.rds")

as.data.frame(fixef(m1)) # Extract "fixed" effects from m1 for plotting the equation 

d <- d %>% 
  mutate(area2_plot = ifelse(area2 == "Cold", "Ref", "Heat"))
  
pscatter <- d %>%
  ungroup() %>%
  data_grid(length = seq_range(length, n = 101),
            area2 = c("Warm", "Cold")) %>%
  mutate(areaC = ifelse(area2 == "Cold", 1, 0),
         areaW = ifelse(area2 == "Warm", 1, 0)) %>%
  add_predicted_draws(m1, re_formula = NA) %>%
  mutate(area2_plot = ifelse(area2 == "Cold", "Ref", "Heat")) %>%
  ggplot(aes(x = length, y = growth, color = area2_plot, fill = area2_plot)) +
  stat_lineribbon(aes(y = .prediction), .width = c(.90), alpha = 1/4) +
  geom_point(data = d, alpha = 0.05, size = 0.8) +
  stat_lineribbon(aes(y = .prediction), .width = 0, alpha = 0.8) +
  scale_fill_manual(values = rev(pal)) +
  scale_color_manual(values = rev(pal)) +
  guides(fill = "none",
         color = guide_legend(override.aes = list(linetype = 0, size = 3, fill = NA,
                                                  shape = 16, alpha = 0.5))) +
  labs(y = expression(paste("Growth [%", yr^-1, "]")),
       x = "Length [cm]", fill = "Area", colour = "Area") +
  annotate("text", 35, 42, label = paste("n=", nrow(dfm), sep = ""), size = 3.5) +
  annotate("text", 35, 36, size = 3.5, color = pal[1],
           label = expression(italic("y=433.45×"~length^-1.18))) + # Cold
  annotate("text", 35, 30, size = 3.5, color = pal[2],
           label = expression(italic("y=509.69×"~length^-1.13))) + # Warm
  theme(text = element_text(size = 12), 
        legend.position = c(0.9, 0.9), 
        legend.spacing.y = unit(0, 'cm'),
        legend.key.size = unit(0, "cm"),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))

# Plot posteriors of parameters
# http://mjskay.github.io/tidybayes/articles/tidy-brms.html

post_alpha <- 
  m1 %>%
  gather_draws(b_alphaC_Intercept, b_alphaW_Intercept) %>%
  ggplot(aes(x = .value, fill = .variable, color = .variable)) +
  stat_halfeye(alpha = 0.5, size = 5, .width = c(0.9)) +
  guides(color = "none", fill = "none") +
  scale_fill_manual(values = pal, labels = c("Cold", "Warm")) +
  scale_color_manual(values = pal) +
  labs(x = expression(italic("\u03B1")), fill = "") +
  theme(legend.position = c(0.9, 0.9),
        legend.key.size = unit(0.2, "cm"),
        legend.background = element_blank())

post_theta <- 
  m1 %>%
  gather_draws(b_thetaC_Intercept, b_thetaW_Intercept) %>%
  ggplot(aes(x = .value, fill = .variable, color = .variable)) +
  stat_halfeye(alpha = 0.5, size = 5, .width = c(0.9)) +
  guides(fill = "none", color = "none") + 
  scale_fill_manual(values = pal, labels = c("Cold", "Warm")) +
  scale_color_manual(values = pal) +
  labs(x = expression(italic("\u03B8")), fill = "") +
  theme(legend.position = c(0.9, 0.9),
        legend.key.size = unit(0.2, "cm"),
        legend.background = element_blank())

# Plot distribution of differences: see statistical rethinging 2 p.157 and:
# https://bookdown.org/content/3890/interactions.html 
# http://mjskay.github.io/tidybayes/articles/tidy-brms.html
diff <- m1 %>%
  spread_draws(b_alphaC_Intercept, b_alphaW_Intercept, b_thetaC_Intercept, b_thetaW_Intercept) %>%
  mutate(diff_alpha = b_alphaW_Intercept - b_alphaC_Intercept,
         diff_theta = b_thetaW_Intercept - b_thetaC_Intercept) 

prop_diff_alpha <- diff %>% 
  summarise(Proportion_of_the_difference_below_0 = sum(diff_alpha < 0) / length(diff_alpha))

prop_diff_theta <- diff %>% 
  summarise(Proportion_of_the_difference_below_0 = sum(diff_theta < 0) / length(diff_theta))

# https://bookdown.org/content/3890/interactions.html
post_diff_alpha <- ggplot(diff, aes(x = diff_alpha, fill = stat(x > 0))) +
  stat_halfeye(alpha = 0.5, size = 5, .width = 0) +
  guides(fill = guide_legend(override.aes = list(size = 1, shape = NA, linetype = 0)), color = "none") + 
  scale_fill_manual(values = c("grey10", "grey70")) +
  annotate("text", 130, 0.95, size = 3, label = paste("prop. diff<0=", round(prop_diff_alpha, 3), sep = "")) +
  labs(x = expression(~italic("\u03B1")[heat]~-~italic("\u03B1")[ref])) +
  theme(legend.position = c(0.2, 0.7),
        legend.key.size = unit(0.2, "cm"),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 10),
        legend.background = element_blank())

post_diff_theta <- ggplot(diff, aes(x = diff_theta, fill = stat(x > 0))) +
  stat_halfeye(alpha = 0.5, size = 5, .width = 0) +
  guides(fill = guide_legend(override.aes = list(size = 1, shape = NA, linetype = 0)), color = "none") + 
  scale_fill_manual(values = c("grey10", "grey70")) +
  annotate("text", 0.07, 0.95, size = 3, label = paste("prop. diff<0=", round(prop_diff_theta, 3), sep = "")) +
  labs(x = expression(~italic("\u03B8")[heat]~-~italic("\u03B8")[ref])) +
  theme(legend.position = c(0.2, 0.7),
        legend.key.size = unit(0.2, "cm"),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 10),
        legend.background = element_blank())

# Plotting all together
pscatter / ((post_alpha/post_diff_alpha) | (post_theta/post_diff_theta)) +
  plot_layout(heights = c(1.2, 1)) +
  plot_annotation(tag_levels = 'A')

ggsave("figures/growth_pred.png", width = 6.5, height = 6.5, dpi = 600)
```

#### Supporting figures
Prior vs posterior
```{r prior vs posterior}
# https://discourse.mc-stan.org/t/presenting-influence-of-different-priors/23393
# Refit model and sample prior or load below (m1_w_prior)
# prior <-
#   prior(normal(500, 100), nlpar = "alphaW") +
#   prior(normal(500, 100), nlpar = "alphaC") +
#   prior(normal(-1.2, 0.3), nlpar = "thetaW") +
#   prior(normal(-1.2, 0.3), nlpar = "thetaC")

# m1_w_prior <- brm(bf(growth ~ areaW*alphaW*length^thetaW + areaC*alphaC*length^thetaC, 
#                      alphaW ~ 1 + (1|birth_year/ID), # parameter varying by ID within birth_year
#                      alphaC ~ 1 + (1|birth_year/ID), # parameter varying by ID within birth_year
#                      thetaW + thetaC ~ 1, nl = TRUE),
#                   family = student(), data = d, prior = prior,
#                   iter = 4000, cores = 3, chains = 3, seed = 9,
#                   save_pars = save_pars(all = TRUE), sample_prior = "yes",
#                   control = list(adapt_delta = 0.99))

# saveRDS(m1_w_prior, "output/growth_scaling/m1_w_prior.rds")
m1_w_prior <- readRDS("output/growth_scaling/m1_w_prior.rds")

# This is just to check variables names in the samples...
# test <- brm(bf(growth ~ areaW*alphaW*length^thetaW + areaC*alphaC*length^thetaC, 
#                alphaW ~ 1,
#                alphaC ~ 1,
#                thetaW + thetaC ~ 1, nl = TRUE),
#             family = student(), data = d, prior = prior,
#             iter = 1, cores = 1, chains = 1, seed = 9,
#             save_pars = save_pars(all = TRUE), sample_prior = "yes",
#             control = list(adapt_delta = 0.99))
# test %>% posterior_samples() %>% clean_names()

post <- m1_w_prior %>%
  posterior_samples() %>%
  clean_names() %>% 
  dplyr::select(b_alpha_w_intercept, b_alpha_c_intercept, prior_b_alpha_w, prior_b_alpha_c,
                b_theta_w_intercept, b_theta_c_intercept, prior_b_theta_w, prior_b_theta_c)

post_long <- post %>% pivot_longer(cols = c(1:8), names_to = "Parameter", values_to = "value")

# parameter "alpha"
prior_post_alpha <- post_long %>%
  filter(Parameter %in% c("b_alpha_w_intercept", "b_alpha_c_intercept", "prior_b_alpha_w", "prior_b_alpha_c")) %>% 
  ggplot(., aes(value, fill = Parameter, color = Parameter, alpha = Parameter))+
  geom_density() +
  labs(x = expression(italic("\u03B1"))) +
  coord_cartesian(expand = 0) +
  scale_alpha_manual(values = c(0.4, 0.4, 0.1, 0.1)) +
  scale_color_manual(values = c(NA, NA, "gray50", "gray50")) +
  scale_fill_manual(values = c(pal[1], pal[2], NA, NA),
                    labels = c(expression(italic("\u03B1")[ref]),
                               expression(italic("\u03B1")[heat]), 
                               expression(paste(Prior~italic("\u03B1")[ref])), 
                               expression(paste(Prior~italic("\u03B1")[heat])))) + 
  guides(color = "none",
         alpha = "none",
         fill = guide_legend(override.aes = list(color = c(NA, NA, "gray50", "gray50"),
                                                 alpha = c(0.4, 0.4, 0.1, 0.1)))) +
  theme(legend.position = c(0.2, 0.8),
        legend.text.align = 0)

# parameter "theta"
prior_post_theta <- post_long %>%
  filter(Parameter %in% c("b_theta_w_intercept", "b_theta_c_intercept", "prior_b_theta_w", "prior_b_theta_c")) %>% 
  ggplot(., aes(value, fill = Parameter, color = Parameter, alpha = Parameter))+
  geom_density() +
  labs(x = expression(italic("\u03B8"))) +
  coord_cartesian(expand = 0) +
  scale_alpha_manual(values = c(0.4, 0.4, 0.1, 0.1)) +
  scale_color_manual(values = c(NA, NA, "gray50", "gray50")) +
  scale_fill_manual(values = c(pal[1], pal[2], NA, NA),
                    labels = c(expression(italic("\u03B8")[ref]),
                               expression(italic("\u03B8")[heat]),
                               expression(paste(Prior~italic("\u03B8")[ref])), 
                               expression(paste(Prior~italic("\u03B8")[heat])))) + 
  guides(color = "none", alpha = "none",
         fill = guide_legend(override.aes = list(color = c(NA, NA, "gray50", "gray50"),
                                                 alpha = c(0.4, 0.4, 0.1, 0.1)))) +
  theme(legend.position = c(0.2, 0.8),
        legend.text.align = 0)

prior_post_theta_ins <- post_long %>%
  filter(Parameter %in% c("b_theta_w_intercept", "b_theta_c_intercept", "prior_b_theta_w", "prior_b_theta_c")) %>% 
  ggplot(., aes(value, fill = Parameter, color = Parameter, alpha = Parameter))+
  geom_density() +
  labs(x = expression(paste(Prior~italic("\u03B8")))) +
  coord_cartesian(expand = 0, ylim = c(0, 1.8), xlim = c(-1.25, -1.05)) +
  scale_alpha_manual(values = c(0.4, 0.4, 0.1, 0.1)) +
  scale_color_manual(values = c(NA, NA, "gray50", "gray50")) +
  scale_fill_manual(values = c(pal[1], pal[2], NA, NA)) + 
  guides(color = "none", fill = "none", alpha = "none")
# prior_post_theta_ins

top <- prior_post_alpha
bottom <- prior_post_theta + inset_element(prior_post_theta_ins, left = 0.55, bottom = 0.3, right = 0.99, top = 0.99)

top / bottom + plot_annotation(tag_levels = list(c('A', 'B'), ''))

ggsave("figures/supp/growth_prior_post.png", width = 6.5, height = 8.5, dpi = 600)
```

Model diagnostics & fit
```{r model diagnostics & fit}
pal_diag <- rev(brewer.pal(n = 3, name = "Dark2"))

# Chain convergence
posterior <- as.array(m1)
dimnames(posterior)

d1 <- mcmc_trace(posterior,
                 pars = c("b_alphaW_Intercept", "b_alphaC_Intercept", "b_thetaW_Intercept", "b_thetaC_Intercept",
                          "sd_birth_year__alphaW_Intercept", "sd_birth_year:ID__alphaW_Intercept",
                          "sd_birth_year__alphaC_Intercept", "sd_birth_year:ID__alphaC_Intercept", 
                          "sigma", "nu"),
                 facet_args = list(ncol = 3, strip.position = "left")) + 
  theme(text = element_text(size = 12),
        strip.text = element_text(size = 3),
        legend.position = "top") + 
  scale_color_manual(values = alpha(pal_diag, alpha = 0.8))

# Resid vs fitted
# The following two plots exhaust the memory, following this helps:
# https://stackoverflow.com/questions/51248293/error-vector-memory-exhausted-limit-reached-r-3-5-0-macos
d2 <- d %>%
  add_residual_draws(m1) %>%
  ggplot(aes(x = .row, y = .residual)) +
  stat_pointinterval(alpha = 0.5, size = 0.7) + 
  theme(text = element_text(size = 12))

# qq-plot
# d3 <- d %>%
#   add_residual_draws(m1) %>%
#   median_qi() %>%
#   ggplot(aes(sample = .residual)) +
#   geom_qq_line() +
#   geom_qq(alpha = 0.8) +
#   theme(text = element_text(size = 12))

# Student QQ plot
# https://stackoverflow.com/questions/42493048/computation-failed-for-stat-summary-what-must-be-a-character-string-or-a-func
# https://www.seascapemodels.org/rstats/2017/10/06/qqplot-non-normal-glm.html

summary(m1)$spec_pars # Extract "fixed" effects from m1 for plotting the equation 
nu <- summary(m1)$spec_pars[2, 1]
nu

# "Base" version
# t <- d %>%
#  add_residual_draws(m1) %>%
#  median_qi()
# resids <- t$.residual
# n <- nrow(d)
# qqplot(qt(ppoints(n), df = nu), resids,
# xlab = "Theoretical quantile", ylab = "residuals")
# qqline(resids, lty = 2)

# Below ggplot version (check they are the same!)
#?geom_qq_line. Does not take a df argument but dparams, a bit strange
d3 <- d %>%
add_residual_draws(m1) %>%
  median_qi() %>%
  ggplot(aes(sample = .residual)) +
  geom_qq_line(distribution = qt, dparams = nu) +
  geom_qq(alpha = 0.8, distribution = qt, dparams = nu) +
  theme(text = element_text(size = 12))

# Posterior predictive
d4 <- pp_check(m1) + 
  theme(text = element_text(size = 12),
        legend.position = c(0.15, 0.95),
        legend.background = element_rect(fill = NA)) + 
  scale_color_manual(values = rev(pal_diag)) +
  labs(color = "")

d1 / (d2 / (d3 + d4)) +
  plot_annotation(tag_levels = 'A')

ggsave("figures/supp/growth_diag_fit.png", width = 6.5, height = 8.5, dpi = 600)
```
